Device fingerprinting for user authentication in web applications \titlenote{(Does NOT produce the permission block, copyright information nor page numbering). For use with ACM\_PROC\_ARTICLE-SP.CLS. Supported by ACM.}

### 2018-11-09 paper.tex

\section{Conclusion}

>>>>

\section{Conclusion}
In a nutshell, device fingerprinting is an effective and convenient method of device identification and we have examined the possibility of transforming this key idea into web-based user authentication using unique hashed fingerprints.

By combining various components of a device's properties, we could increase the fingerprint entropy as well as obtain a hash unqiue for an individual's device, correspondingly unique to an individual.

Although an device's fingerprint could change over time, we have considered that a user can be re-authenticated using a one-time password sent to their registered email.

It is worth noting that fingerprinting alone however, cannot prevent attacks such as session hijacking where a perpetrator can simply collect additional information about the target device once the hijacking is successful.

All in all, we think that fingerprinting is useful and provides a viable authentication method allowing users to be authenticated easily and such technology can be explored further in future security implementations.
